Notes on generating initial models for mapping into {\tt MAESTRO}

### 2008-08-14 docs/initial_models/paper.tex
minor fixes

\section{Creating the initial model}
\begin{itemize}
\item The initial model should be but into HSE according to $(p_{i+1} - p_i)/\Delta r = half (\rho_{i+1} - \rho_i) g_{i+\half}$

@@

\section{Spherical notes}
\begin{itemize}
\item Spherical runs use $p$, $(\rho X)$, and $\rho$ from the initial model.  These are then
mapped onto the Cartesian grid, and then $(rho h)$ is computed via the EOS.
\end{itemize}

>>>>

\section{Creating the initial model}
\begin{itemize}
\item The initial model should be but into HSE according to $(p_{i+1} - p_i)/\Delta r = \half (\rho_{i+1} - \rho_i) g_{i+\half}$

@@

\section{Spherical notes}
\begin{itemize}
\item Spherical runs use $p$, $(\rho X)$, and $\rho$ from the initial model.  These are then
mapped onto the Cartesian grid, and then $(\rho h)$ is computed via the EOS.
\end{itemize}
